
\chapter{Example Datapoint}
\label{example_datapoint}
% Figure \ref{lst:single_point} shows a real example of a datapoint in YAML markup. 
% Different parts of the data were used in the investigation.
\begin{listing}[h!]
\begin{minted}[]{yaml}
-   arg_name: tensors                                 # argument name: STRING
    arg_desc: ' a list of variable or op tensors.'    # argument description: STRING
    arg_type: null                                    # argument type: STRING or NULL
    args: [tensors, prefix]                           # list of arguments: LIST of STRING
    arg_info:                                         # info on other arguments: DICT of DICT
        prefix: 
            desc: ' An optional prefix for the summary names.' 
            type: null
    filename: /tensorflow/contrib/slim/python/slim/summaries.py  # filename: STRING
    name: add_zero_fraction_summaries                 # function name: STRING 
    sig: (tensors, prefix=None)                       # function signature: STRING
    pkg: tensorflow                                   # library: STRING  
    src: |                                            # source code: STRING 
      def add_zero_fraction_summaries(tensors, prefix=None):
        """Adds a scalar zero-fraction summary for each of the given tensors.
  
        Args:
          tensors: a list of variable or op tensors.
          prefix: An optional prefix for the summary names.
  
        Returns:
          A list of scalar `Tensors` of type `string` whose contents are the
          serialized `Summary` protocol buffer.
        """
        summary_ops = []
        for tensor in tensors:
          summary_ops.append(add_zero_fraction_summary(tensor, prefix=prefix))
        return summary_ops
    docstring: |                                      # sphinx annotated docstring: STRING 
      Adds a scalar zero-fraction summary for each of the given tensors.

      :param tensors: a list of variable or op tensors.
      :param prefix: An optional prefix for the summary names.

      :returns: A list of scalar `Tensors` of type `string` whose contents are the
                 serialized `Summary` protocol buffer.
\end{minted}
     \caption{Real example of a single data point, with all metadata. The docstring in the source has been elided for brevity}
     \label{lst:single_point}
\end{listing}